Normalization Reweighting

### 2022-05-03 manuscript.Rmd
Update manuscript.Rmd
Fixed weird commit issues

runcode <- 1  # this flag chooses whether to run the underlying analysis code (1), or just load in the figures from the last time this was run (0)
processraw <- 0  # this flag determines whether the raw data are downloaded from OSF and processed - this will require ~30GB of hard drive space and take several hours

@@

@@

@@

      # epoch the data, Fourier transform and store
      triggertimes <- (1:40) * 0
      counter <- 0
      for (n in 1:nrow(EEGdata)) {
        if (EEGdata$Trigger[n] %in% legaltriggers) {
          counter <- counter + 1
          triggertimes[counter] <- n
        }
      }

@@

if (runcode==1){
  d <- dir('temp/VilidaiteProcessed/')

@@

@@

f1 <- 7
f2 <- 5
    binwidth <- 1000
    tindex <- 1 + f1*(binwidth/1000)
    mindex <- 1 + f2*(binwidth/1000)
condlist <- c(6,8,13)
targetchannels <- match(targetelectrodes, electrodes) - 2
d <- dir('temp/VilidaiteProcessed/')
all7Hz <- array(0,dim=c(length(d),14,64))
all5Hz <- array(0,dim=c(length(d),14,64))
timecourse7Hz <- array(0,dim=c(length(d),3,14000))
timecourse5Hz <- array(0,dim=c(length(d),3,14000))

>>>>

runcode <- 1  # this flag chooses whether to run the underlying analysis code (1), or just load in the figures from the last time this was run (0)
processraw <- 1  # this flag determines whether the raw data are downloaded from OSF and processed - this will require ~30GB of hard drive space and take several hours

@@

osfnode <- 'y4n5k'    # this is where the pilot data are stored
osfproject <- osf_retrieve_node(osfnode)
EEGfiles <- osf_ls_files(osfproject,n_max=300)

@@

    if (s < 10){tarname <- paste0('S0', s, '.tar')}
    if (s > 9){tarname <- paste0('S', s, '.tar')}

    if (!file.exists(paste0(datadir,tarname))){
      fid <- which(EEGfiles$name==tarname)
      osf_download(EEGfiles[fid,],datadir,progress=TRUE)
    }

    condcounter <- (1:20) * 0
    allsamples <- array(0, dim = c(10,20,64,duration*samplerate))

    untar(paste0(datadir,tarname),exdir=tempdir)

@@

      # epoch the data, Fourier transform and store
      triggertimes <- (1:40) * 0
      counter <- 0
      for (n in 1000:nrow(EEGdata)) {    # ignore triggers starting in the first 1000ms that generate an error
      for (n in 1:nrow(EEGdata)) {
        if (EEGdata$Trigger[n] %in% legaltriggers) {
          counter <- counter + 1
          triggertimes[counter] <- n
        }
      }

@@

if (runcode==1){
#   d <- dir('temp/VilidaiteProcessed/')
#   
#   allwaves <- array(0,dim=c(length(d),14,64,14000))
#   for (s in 1:length(d)){
#     load(paste0('temp/VilidaiteProcessed/',d[s]))
#     allwaves[s,,,] <- meanwaveforms
#   }
#   
#   meanwaveforms <- array(0,dim=c(14,64,14000))
#   alltarget <- matrix(0,nrow=14,ncol=64)
#   allmask <- matrix(0,nrow=14,ncol=64)
#     for (cond in 1:14){
#       for (ch in 1:64){
#         temp <- allwaves[,cond,ch,]
#         allspec <- matrix(0,nrow=length(d),ncol=10000)
#         for (subj in 1:length(d)){
#           allspec[subj,] <- fft(temp[subj,2001:12000])/10000
#         }
#         targetresps <- allspec[,tindex]
#         maskresps <- allspec[,mindex]
#       if (sum(abs(targetresps))>0){  
#       tempxy <- data.frame(Re(targetresps),Im(targetresps))
#       D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
#       i1 <- (D<3)
#       tempxy <- data.frame(Re(maskresps),Im(maskresps))
#       D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
#       i2 <- (D<3)
#       i <- which((i1*i2)>0)
#         meanwaveforms[cond,ch,] <- colMeans(temp[i,])
#       }
#         spec <- fft(meanwaveforms[cond,ch,2001:12000])/10000
#         alltarget[cond,ch] <- spec[tindex]
#         allmask[cond,ch] <- spec[mindex]
#       }
#     }
#   
# }
# 
# targetchannels <- match(targetelectrodes, electrodes) - 2
# 
# elecave <- colMeans(meanwaveforms[6,targetchannels,])
# binwidth <- 1000
# f1 <- 7
# tindex <- 1 + f1*(binwidth/1000)
# fspec <- elecave*0
# for (t in 1:(length(elecave)-binwidth)){
#   temp <- elecave[t:(t+binwidth-1)]
#   spec <- fft(temp)/binwidth
#   fspec[t] <- abs(spec[tindex])
# }
# elecave <- colMeans(meanwaveforms[13,targetchannels,])
# binwidth <- 1000
# f1 <- 7
# tindex <- 1 + f1*(binwidth/1000)
# fspec2 <- elecave*0
# for (t in 1:(length(elecave)-binwidth)){
#   temp <- elecave[t:(t+binwidth-1)]
#   spec <- fft(temp)/binwidth
#   fspec2[t] <- abs(spec[tindex])
# }
# 
# times <- -499:13500
# plot(times,fspec,type='l',col='red')
# lines(times,fspec2,col='green')
  d <- dir('temp/VilidaiteProcessed/')

@@

# temp <- allwaves[,6,,2001:12000]
# meantemp <- apply(allwaves,2:3,mean)

@@

f1 <- 7
f2 <- 5
    binwidth <- 1000
    tindex <- 1 + f1*(binwidth/1000)
    mindex <- 1 + f2*(binwidth/1000)
condlist <- c(6,8,13)

targetchannels <- match(targetelectrodes, electrodes) - 2
d <- dir('temp/VilidaiteProcessed/')
all7Hz <- array(0,dim=c(length(d),14,64))
all5Hz <- array(0,dim=c(length(d),14,64))
timecourse7Hz <- array(0,dim=c(length(d),3,14000))
timecourse5Hz <- array(0,dim=c(length(d),3,14000))
